A Stopped Negative Binomial Distribution

### 2016-06-20 stat-and-prob-letters/snb-paper.tex
Plots and captions are based on SNB(.2, 7, 11).

\begin{figure}[bp!]
\centering
\includegraphics[width=\textwidth]{snb-first-plot.pdf}
\caption{
The probability mass function for a trial where $p$ 
is 0.045 and where the trial stops
after two patients respond or 11 patients do not respond.
}
\label{fig:first-plot}
\end{figure}

More generally the distribution for number of trial enrollments is shown in 
Fig.~\ref{fig:first-plot}. The probability mass is concentrated at the 
$11^{\text{th}}$ and $12^{\text{th}}$ step since $p$ 
is small and for most realizations reach 11 
non-responders before reaching 2 responders.

\begin{figure}[bp!]
\centering
\subfloat[Expected value]{\includegraphics[width=0.5\textwidth]{dist-mean.pdf}}
\hfill
\subfloat[Variance]{\includegraphics[width=0.5\textwidth]{dist-var.pdf}}
\caption{
The mean and variance for a trial that stops after two patients respond
or 11 patients do not respond when $p$ varies between zero and one.
}
\label{fig:exp-and-var}
\end{figure}

@@

\begin{figure}[t!]
\centering
\subfloat[The SNB distribution.]{\includegraphics[width=0.5\textwidth]{snb_density.pdf}}
\hfill
\subfloat[The Binomial distribution.]{\includegraphics[width=0.5\textwidth]{bin_density.pdf}}
\caption{
SNB(0.045, 2, 11) with mass contributed from 
$s$ successes (black) or $t$ failures (grey) along with Bin(0.045, 12) with
at least 2 successes (black) or fewer (grey).
}
\label{fig:snb_bin_compare}
\end{figure}

@@

\begin{figure}[h!]
\centering
\subfloat[The compound distribution's expected sample size.]{\includegraphics[width=0.5\textwidth]{bayesian-sample-expectation.pdf}}
\hfill
\subfloat[The compound distribution's variance.]{\includegraphics[width=0.5\textwidth]{bayesian-sample-variance.pdf}}
\caption{
The expected size and variance of the compound SNB with $s=2$, $t=11$
with $\mathbb{E}\ p = 0.045$ varying the uncertainty 
in the distribution of $p$. A larger value of $c$
corresponds to a Beta with smaller variance.
}
\label{fig:bayesian-sample-size}
\end{figure}

>>>>

%\begin{figure}[bp!]
%\centering
%\includegraphics[width=\textwidth]{snb-first-plot.pdf}
%\caption{
%The probability mass function for a trial where $p$ 
%is 0.045 and where the trial stops
%after two patients respond or 11 patients do not respond.
%}
%\label{fig:first-plot}
%\end{figure}

\begin{figure}[bp!]
\centering
\subfloat[enrollment distribution]{\includegraphics[width=0.5\textwidth]{snb-first-plot.pdf}}
\hfill
\subfloat[effect of varying $p$]{\includegraphics[width=0.5\textwidth]{mean-and-variance.pdf}}
\caption{
The distribution of a trial that stops after seven patients respond
or 11 patients do not. (a) shows the distribution when
$p = 0.2$. (b) shows the result of varying $p$ between 
zero and one.
}
\label{fig:exp-and-var}
\end{figure}

More generally the distribution for number of trial enrollments is shown in 
Fig.~\ref{fig:first-plot} (a). The probability mass is concentrated at the 
$11^{\text{th}}$ and $12^{\text{th}}$ step since $p$ 
is small and for most realizations reach 11 
non-responders before reaching 2 responders.

@@

\begin{figure}[t!]
\centering
\subfloat[SNB distribution]{\includegraphics[width=0.5\textwidth]{snb_density.pdf}}
\hfill
\subfloat[Binomial distribution.]{\includegraphics[width=0.5\textwidth]{bin_density.pdf}}
\caption{
SNB(0.045, 2, 11) with mass contributed from 
$s$ successes (black) or $t$ failures (grey) along with Bin(0.045, 12) with
at least 2 successes (black) or fewer (grey).
}
\label{fig:snb_bin_compare}
\end{figure}

@@

\begin{figure}[h!]
\centering
\subfloat[mean]{\includegraphics[width=0.5\textwidth]{bayesian-sample-expectation.pdf}}
\hfill
\subfloat[variance]{\includegraphics[width=0.5\textwidth]{bayesian-sample-variance.pdf}}
\caption{
The expected size and variance of the compound SNB with $s=2$, $t=11$
with $\mathbb{E}\ p = 0.045$ varying the uncertainty 
in the distribution of $p$. A larger value of $c$
corresponds to a Beta with smaller variance.
}
\label{fig:bayesian-sample-size}
\end{figure}
